---
title: "R Markdown Presentation & Plotly"
author: Ivan Castillo
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

##Instructions

Create a web page presentation using R Markdown that features a plot created with Plotly. Host your webpage on either GitHub Pages, RPubs, or NeoCities.

Your webpage must contain the date that you created the document, and it must contain a plot created with Plotly. We would love to see you show off your creativity!

## US unemployment rate time series

Using economic data from united states included in ggplot2 package, we can calculate chronologically the unemployment rate in US.

```{r warning=FALSE, message=FALSE}
library(plotly)
p <- plot_ly(economics, x = ~date, y = ~unemploy / pop)
htmltools::tagList(list(p, p))
```

## US economic time series data

### Description

This dataset was produced from US economic time series data available from http://research.stlouisfed.org/fred2. economics is in "wide" format, economics_long is in "long" format.

### Variables

+ _date:_ Month of data collection

+ _unemploy:_ Number of unemployed in thousands

+ _pop:_ Total population, in thousands

